Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-14 paper.qmd
Added figure 10

<!--Projection with tSNE-->
```{r}
#| label: five-gau-proj-tsne-model

@@

projection <- cbind(
  c(0.28321,-0.28851,-0.67413,0.39226),
  c(-0.70800,-0.44269,0.04835,0.26867))

five_gau_proj_tsne_model <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
) +
  xlim(c(-0.15, 0.15)) +
  ylim(c(-0.15, 0.15))
```

```{r}
#| label: fig-five-gau-projs
#| fig-cap: "(a) tSNE"

five_gau_proj_tsne_model
```

>>>>

<!--Projections-->
```{r}
#| label: five-gau-proj-tsne-model

@@

projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558,-0.23854,-0.63659,0.35753))

five_gau_proj_tsne_model <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55))
```

```{r}
#| label: five-gau-proj-umap-model

umap_data_gau <- read_rds("data/five_gau_clusters/umap_data_five_gau.rds")
gau1_scaled_obj <- gen_scaled_data(
  data = umap_data_gau)
umap_gau_scaled <- gau1_scaled_obj$scaled_nldr

## Compute hexbin parameters
num_bins_x_gau1 <- 44
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

gau1_model <- fit_highd_model(
  training_data = training_data_gau,
  emb_df = umap_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = FALSE,
  col_start_highd = "x"
)

## Hexagonal binning to have regular hexagons
hb_obj_gau1 <- hex_binning(
  data = umap_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1)

umap_data_with_hb_id <- hb_obj_gau1$data_hb_id

df_all_gau1 <- dplyr::bind_cols(training_data_gau |> dplyr::select(-ID),
                                umap_data_with_hb_id)

projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558,-0.23854,-0.63659,0.35753))

five_gau_proj_umap_model <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55))
```

```{r}
#| label: five-gau-proj-pacmap-model

pacmap_data_gau <- read_rds("data/five_gau_clusters/pacmap_data_five_gau.rds")
gau1_scaled_obj <- gen_scaled_data(
  data = pacmap_data_gau)
pacmap_gau_scaled <- gau1_scaled_obj$scaled_nldr

## Compute hexbin parameters
num_bins_x_gau1 <- 21
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

gau1_model <- fit_highd_model(
  training_data = training_data_gau,
  emb_df = pacmap_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  is_bin_centroid = TRUE,
  is_rm_lwd_hex = FALSE,
  col_start_highd = "x",
  q = 0.14
)

## Hexagonal binning to have regular hexagons
hb_obj_gau1 <- hex_binning(
  data = pacmap_gau_scaled,
  bin1 = num_bins_x_gau1,
  r2 = r2_gau1,
  q = 0.14)

pacmap_data_with_hb_id <- hb_obj_gau1$data_hb_id

df_all_gau1 <- dplyr::bind_cols(training_data_gau |> dplyr::select(-ID),
                                pacmap_data_with_hb_id)

projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558,-0.23854,-0.63659,0.35753))

five_gau_proj_pacmap_model <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55))
```

```{r}
#| label: fig-five-gau-projs
#| fig-height: 6
#| fig-width: 18
#| fig-cap: "(a) tSNE, (b) UMAP, and (c) PaCMAP"

five_gau_proj_tsne_model + five_gau_proj_umap_model + five_gau_proj_pacmap_model +
  plot_layout(guides = "collect", ncol = 3) &
  theme(legend.position='none')
```
